Programming Language Foundations in Agda

### 2019-07-11 papers/scp/PLFA.tex
progress on my updates to section 2

\author[adr1]{Wen Kokke}
\ead{wen.kokke@ed.ac.uk}
\author[adr2]{Jeremy Siek}
\ead{jsiek@indiana.edu}
\author[adr1]{Philip Wadler\corref{cor1}}
\ead{wadler@inf.ed.ac.uk}
\cortext[cor1]{Corresponding author}

@@

>>>>

\author[adr1]{Wen Kokke}
\ead{wen.kokke@ed.ac.uk}
\author[adr2]{Jeremy G. Siek}
\ead{jsiek@indiana.edu}
\author[adr1]{Philip Wadler\corref{cor1}}
\ead{wadler@inf.ed.ac.uk}
\cortext[cor1]{Corresponding author}

@@

\paragraph{Substitution: in the untyped lambda calculus}
Delves deeper into the properties of simultaneous substitution,
establishing the equations of the $\sigma$ algebra of
\citet{Abadi-1991}. These equations enable a straightforward proof of
the Substitution Lemma~\citep{Barendregt-1984}, which is needed in the
next chapter.

\paragraph{Confluence: of the untyped lambda calculus}
Presents a proof of the Church-Rosser theorem based on the classic
idea of parallel reduction due to Tait and Martin-L\"of. The proof in
Agda is streamlined by the use of ideas from
\citet{Schafer-Tebbi-Smolka-2015} and \citet{Pfenning-1992}.

\paragraph{Big-step: evaluation for call-by-name}
Introduces the notion of big-step evaluation to develop a
deterministic call-by-name reduction strategy. The main result of this
chapter is a proof that big-step evaluation implies the existence of a
reduction sequence that terminates with a lambda abstraction.

\subsection*{Part III, Denotational Semantics}

\paragraph{Denotational: semantics of the untyped lambda calculus}
The early denotational semantics of the lambda calculus based on graph
models~\citep{Scott-1976,Engeler-1981,Plotkin-1993} and filter
models~\citep{Barendregt-1983} were particularly simple and elegant.
This chapter presents such a semantics in a big-step style that is
approachable to readers familiar with operational semantics.

\paragraph{Compositional: the denotational semantics is compositional}
TODO

\paragraph{Soundness: of reduction with respect to denotational semantics}
TODO

\paragraph{Adequacy: of denotational semantics with respect to reduction}
TODO

\paragraph{Contextual Equivalence: is implied by denotational equality}
TODO
